\documentclass{article}
\usepackage[utf8]{inputenc}

\title{}
\author{}
\date{}

\begin{document}

\maketitle 

\pagebreak

\section{Description}

\paragraph{In recent years, increases in memory subsystem speed have not kept pace with the increase in
processor speed, causing processor execution rates to become increasingly limited by the latency
of accessing instructions and data. On-chip caches are a popular technique to combat this speed
mismatch. As integrated circuits become denser, designers have more chip area that can be
devoted to on-chip caches. Straight-forward scaling of cache sizes as the available area in-
creases, however, may not be the best solution, since the larger a cache, the larger its access
time. Using cache hierarchies (two or more levels) is a potential solution. This paper explores
the tradeoffs in the design of on-chip microprocessor caches for a range of available on-chip
cache areas.}
\paragraph{There are a number of potential advantages of two-level on-chip caching with a mixed (in-
struction and data) second-level cache over single-level on-chip caching. First, the primary
cache (also referred to as the L1 cache) usually needs to be split into separate instruction and
data caches to support the instruction and data fetch bandwidths of modern processors. By having a
 two-level hierarchy on-chip where the majority of the
cache capacity is in a mixed second-level cache (L2 cache), cache lines are dynamically al-
located to contain data or instructions depending on the program’s requirements, as opposed to
living with a static partition given by single-level on-chip cache sizes chosen at design time.}

\paragraph{A second and more important potential advantage of two-level on-chip caching is an improve-
ment in cache access time. As existing processors with single-level on-chip caching are shrunk
to smaller lithographic feature sizes. If the additional area available due to a process shrink is used 
to simply extend the first-level cache sizes, the caches will get
slower relative to the processor datapath. Instead, if the extra area is used to hold a second-level
cache, the primary caches can scale in access time along with the datapath, while additional
cache capacity is still added on-chip.}

\paragraph{A third potential advantage of two-level cache structures is that the second-level cache can be
made set-associative while keeping the primary caches direct-mapped. This keeps the fast
primary access time of direct-mapped caches, but reduces the penalty of first-level conflict
misses since many of these can be satisfied from an on-chip set-associative cache instead of
requiring an off-chip access.}

\paragraph{When primary cache sizes are less than or equal to the page size, address translation can easily
occur in parallel with a cache access. However, most modern machines have minimum page
sizes of between 4KB and 8KB. This is smaller than most on-chip caches. By using two-level
on-chip caching, the primary caches can be made less than or equal to the page size, with the
remaining on-chip memory capacity being devoted to the second-level cache. This allows the
address translation and first-level cache access to occur in parallel. This is a fourth potential advantage of 
two-level cache structures.}

\paragraph{A fifth advantage of two-level cache structures is that a chip with a two-level cache will
usually use less power that one with a single-level organization (assuming the area devoted to the
cache is the same). In a single-level configuration, wordlines and bitlines are longer, meaning
there is a larger capacitance that needs to be charged or discharged with every cache access. In a
two-level configuration, most accesses only require an access to a small first-level cache.}

\pagebreak

\section{Why topic is interesting and important ?}

\paragraph{Several trends in current technology have increased the vi-
ability of a two-level cache, for example:}

\begin{itemize}

    \item Technology is yielding impressive reductions in processor
    speed, but memory speed has not kept pace. Therefore,
    the disparity between processor and memory speed is in-
    creasing.

    \item The appetite for memory is rapidly increasing and pri-
    mary memories of 100s to 1000s of megabytes will be
    common. Larger memories typically have larger access
    times because of packaging and physical constraints.

    \item As on-chip densities increase, it becomes possible to in-
    clude small on-chip instruction and/or data caches. These caches will need to be backed up by larger
    second-level caches. As one example, the MicroVAX 3500
    has a 1K on-chip cache and a 64K second-level cache.

    \item Shared memory multiprocessors require local caches to
    reduce bus contention. A second-level global cache can
    help to further reduce access time on cache misses.
    
\end{itemize}

\paragraph{Therefore, from the above points it sums up that processors have more than
 one level cache in order to increase the capacity of the processor cache without also
 dramatically increasing the price of the processor. This careful mixture allows for 
 processors that are faster and cheaper. 
}

\paragraph{Cache memory is very useful because it saves the computer user a lot of time in 
    opening common data and giving common commands. Cache memory is very convinient 
    because opening data in cache is dramatically faster than opening data in the main 
    hard disk. Because of this utter importance of cache it is really necessary to discuss 
    on this topic and bring out some revolutionary improvement in this area.
}


\section{Conclusion}

\paragraph{We have studied several aspects of two-leve cache memories in uniprocessors.We have 
modeled the miss rate, cache area, and cache access time to achieve a solid basis to
study on-chip memory system tradeoffs.}

\paragraph{An extra level of cache memory can provide a worthwhile 
performance gain when used with proper combinations
of small first-level caches and large main memory access times.
Two-level on-chip cache hierarchies perform even better in low-cost 
systems without a board-level cache.}

\paragraph{Combining this with set-associative second-level caches 
improves performance even further. This is because the increase in 
capacity provided by two-level exclusive caching increases as the 
second level of caching is made more associative.}

\paragraph{Write-back strategies were studied for both cache levels. 
The best performance is provided by write-back at both levels
The principal effect of write-back was the reduction of write 
bandwidth required at the next higher level of memory.}

\paragraph{If only one of the caches were to use write-back,then write-back
should be included in the L1 cache because}

\begin{itemize}
    \item The L1 cache typically has a faster access time, and writes
    could be processed more quickly without buffering, and

    \item The L1 cache is smaller than the L2 cache.

\end{itemize}

\paragraph{Lastely, multilevel caches provide a fruitful 
area for study, and much more needs to be done.}

\paragraph{Certainly an important area for further evaluation 
is multi-level caches in multiprocessors. In this study, we concentrated
on only 2-level Cache.}

\end{document}
